SKETCH RECOGNITION AND UNDERSTANDING

### 2009-10-13 draft/chapterSurvey.tex
FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL FINAL

 Agar et al. \cite{polygonfeedback31} used the time-stamp for each point and compute time difference between every two successive point to help him find corners as he argued that it provides more distinct maximum than the speed information. He mentions that the pointing device (for example the mouse) sampling rate is the reason for this phenomena. The points are sampled at regular time intervals while the pointing device is moving. There are no points while the pointing device is stationary. This leads to a nearly constant time difference between samples while the pen is moving and large difference while the pen is stationary. Contrary to speed information, where the user draws with variant speeds which tends to make the speed information include a lot of noise in the data.

Sezgin et al.\cite{earlyprocess} used both speed and direction information. Their system gives better results than using only speed or direction information. This is because the speed information tend to be noisy when drawing large symbols, on the other side when using only direction information the some corner are missed. Our system uses speed, direction and time difference information in its preliminary calculation step. This ensures that all the possible vertices are considered when the segmentation algorithm segments strokes. %both speed and direction information help detecting vertices when the

@@

Arvo \cite{Fluid25} Tried to combine fast morphing and basic recognition for the sketch drawn as the user draw it. It tries to move the points of strokes drawn by the user draw into one of the known shapes (ex: box, lines and circle). It uses a relaxation and least square method for circles and uses the string of forces for finding best-fit box. However, their system can only identify circle and rectangles drawn using a single stroke.  
\begin{figure}
	\centering
	\subfigure[Feature area of line an arc]{
		\includegraphics{images/featurearearc.eps}}
		\subfigure[Feature area of line]{
				\includegraphics{images/featureareline.eps}}
	\caption[Feature Area]{Feature Area \cite{meanshift10}}
	\label{fig:featurearearc}
\end{figure}

@@

In all of these system only \cite{SketchRead2007} using stroke based recognition have been implemented to the fully create a system that free draw sketch and understand them. This is because the emphasis on the interactive side of the sketch system which result in large difficulties in processing free hand sketches. Methods based on gesture and global stroke properties produce systems that are dependent on assumptions about how strokes can be grouped. These systems assume that users will finish drawing a shape before moving to the next one \cite{multistrokeEvaluation,Cali63,geometrydomain49}. This let them to temporally group strokes and then recognizes them based on their strokes or global shape properties. \cite{AlvaradoDigital} argued that this assumption does not hold in natural sketches.

@@

To avoid most problems in such system, our system uses hybrid of both global shape and hierarchical description methods. Currently, our system recognize independent symbols. Each symbol is segmented and hierarchical features are computed.  Features that are representing the global description of the shape are also generated and appended to the hierarchical features. Recognition is done using SVM Linear classifier as it proved to be one of the best learning algorithms. 
%*********************************************************************************************5&&&&&&&&&&&&&&&&&&&&
%*********************************************************************************************5&&&&&&&&&&&&&&&&&&&&
%*********************************************************************************************5&&&&&&&&&&&&&&&&&&&&
%*********************************************************************************************5&&&&&&&&&&&&&&&&&&&&
%*********************************************************************************************5&&&&&&&&&&&&&&&&&&&&
\chapter{Particle Swarm Optimization}
\label{sec:ParticleSwramOptimization}

@@

\subsection{PSO vs. GA}
 PSO can be viewed as an algorithm between stochastic search and Evolutionary algorithms\cite{PSOpattern}. In general the PSO is a continuous optimization problem but experiments showed it performed as well as GA which is in general a discrete and binary optimization problem. In general, both GA and PSO share many points, e.g, both algorithms generate the initial population randomly, both use a fitness function or value to evaluate the goodness of solutions and the next populations. Nevertheless, PSO dose not have genetic operators like crossover or mutations. Particles are updated by internal communication among themselves based on the local and global best. In contrast to GA where chromosomes shares information with each others, PSO shares information using memory from previous iteration in form of global best solution. This leads the population to move as one group to towards an optimal solution (i.e find solution quickly). %which significally

  %From the procedure, we can learn that PSO shares many common points with GA. Both algorithms start with a group of a randomly generated population, both have fitness values to evaluate the population. Both update the population and search for the optimium with random techniques. Both systems do not guarantee success.

@@

This section will describe each step of the PSO Algorithm. Figure\ref{fig:BlockPSO} illustrates the DPSO algorithm in Algorithm \ref{DPSOalg} steps in details. Initially, the swarm particles are created and each of which is a binary vector corresponding to candidate solution. Additionally, the velocities of each particle is initialized at random by drawing uniformly real values from the range [0.0 to 1.0]. Then the evolutionary process of particle movement is iterated until maximum number of iteration or a fitness error achieved. At each iteration,  the fitness value of each particle is evaluated, and the particles individual local best and global best is updated. The particle position is adjusted as follow; the velocities is computed using Equation \ref{eq:Swarm}. Equation \ref{eq:vmax} is used to scale the velocity to values between 0 and 1 which will serve as a probability that the corresponding bit takes the value of 1. The particles bit vectors are updated by Equation \ref{eq:descrite} according to their velocity which measure the trajectory to the target solution based on local experience ($lbest_{i}$) and global intelligence ($gbest_{i}$). Before the end of the iteration the particle may move to a refined location based on the refine procedure used. 
\begin{algorithm}
\caption{ Discrete Particle Swarm Algorithm }
\label{DPSOalg}
\begin{verbatim}
Initialize 
  1. Generate N particles with M dimensions (P_i...P_N) 
  2. Generate velocities for each particle for M dimension randomly. 
  3. Repeat till Maximum number of iteration OR ErrorThreshold  
         For each particle P_i do the following 
         3.a   Compute fitness  (fitness)
         3.b   Determine Lbest  
               if (lbest_fitness<fitness)
                  3.b.1   lbest=P_i
         3.c      Determine Gbest.
               if (lGest_fitness<fitness)
                  3.c.1   lGest=P_i
         3.d   Compute the Velocity for each dimension using eq.3.2 
         3.e   Bound Velocity using eq.3.4
         3.f   Update particle values using eq. 3.3
         3.g   Refine the location of the particle
         end .
     end 
4. return Gbest
\end{verbatim}
  \end{algorithm}

>>>>

 Agar et al. \cite{polygonfeedback31} used the time-stamp for each point and compute time difference between every two successive point to help him find corners as he argued that it provides more distinct maximum than the speed information. He mentions that the pointing device (for example the mouse) sampling rate is the reason for this phenomena. The points are sampled at regular time intervals while the pointing device is moving. There are no points while the pointing device is stationary. This leads to a nearly constant time difference between samples while the pen is moving and large difference while the pen is stationary. Contrary to speed information, where the user draws with variant speed, which tends to make the speed information include a lot of noise in the data.

Sezgin et al.\cite{earlyprocess} used both speed and direction information. Their system gives better results than using only speed or direction information. This is because the speed information tends to be noisy when drawing large symbols, on the other side when using only direction information the some corner are missed. Our system uses speed, direction and time difference information in its preliminary calculation step. This ensures that all the possible vertices are considered when the segmentation algorithm segments strokes. %both speed and direction information help detecting vertices when the

@@

Arvo \cite{Fluid25} tried to combine fast morphing and basic recognition for the sketch drawn as the user draws it. It tries to move the points of strokes drawn by the user draw into one of the known shapes (ex: box, lines and circle). It uses a relaxation and least square method for circles and uses the string of forces for finding best-fit box. However, their system can only identify circle and rectangles drawn using a single stroke.  
\begin{figure}
	\centering
	\subfigure[Feature area of line an arc]{
		\includegraphics{images/featurearearc.eps}}
		\subfigure[Feature area of line]{
				\includegraphics{images/featureareline.eps}}
	\caption[Feature Area]{Feature Area \cite{meanshift10}}
	\label{fig:featurearearc}
\end{figure}

@@

In all of these system only \cite{SketchRead2007} using stroke based recognition have been implemented to the fully create a system that free draw sketch and understand them. This is because the emphasis on the interactive side of the sketch system which results in large difficulties in processing free hand sketches. Methods based on gesture and global stroke properties produce systems that are dependent on assumptions about how strokes can be grouped. These systems assume that users will finish drawing a shape before moving to the next one \cite{multistrokeEvaluation,Cali63,geometrydomain49}. This let them to temporally group strokes and then recognizes them based on their strokes or global shape properties. \cite{AlvaradoDigital} argued that this assumption does not hold in natural sketches.

@@

To avoid most problems in such system, our system uses hybrid of both global shape and hierarchical description methods. Currently, our system recognizes independent symbols. Each symbol is segmented and hierarchical features are computed.  Features that are representing the global description of the shape are also generated and appended to the hierarchical features. Recognition is done using SVM Linear classifier as it proved to be one of the best learning algorithms. 
%*********************************************************************************************5&&&&&&&&&&&&&&&&&&&&
%*********************************************************************************************5&&&&&&&&&&&&&&&&&&&&
%*********************************************************************************************5&&&&&&&&&&&&&&&&&&&&
%*********************************************************************************************5&&&&&&&&&&&&&&&&&&&&
%*********************************************************************************************5&&&&&&&&&&&&&&&&&&&&
\chapter{Particle Swarm Optimization}
\label{sec:ParticleSwramOptimization}

@@

\subsection{PSO vs. GA}
 PSO can be viewed as an algorithm between stochastic search and Evolutionary algorithms\cite{PSOpattern}. In general the PSO is a continuous optimization problem but experiments showed it performed as well as GA which is in general a discrete and binary optimization problem. In general, both GA and PSO share many points, e.g, both algorithms generate the initial population randomly; both use a fitness function or value to evaluate the goodness of solutions and the next populations. Nevertheless, PSO does not have genetic operators like crossover or mutations. Particles are updated by internal communication among themselves based on the local and global best. In contrast to GA where chromosomes shares information with each others, PSO shares information using memory from previous iteration in form of global best solution. This leads the population to move as one group to towards an optimal solution (i.e find solution quickly). %which significally

  %From the procedure, we can learn that PSO shares many common points with GA. Both algorithms start with a group of a randomly generated population, both have fitness values to evaluate the population. Both update the population and search for the optimum with random techniques. Both systems do not guarantee success.

@@

This section will describe each step of the PSO Algorithm. Figure\ref{fig:BlockPSO} illustrates the DPSO algorithm in Algorithm \ref{DPSOalg} steps in details. Initially, the swarm particles are created and each of which is a binary vector corresponding to candidate solution. Additionally, the velocities of each particle are initialized at random by drawing uniformly real values from the range [0.0 to 1.0]. Then the evolutionary process of particle movement is iterated until maximum number of iteration or a fitness error achieved. At the beginning of each iteration, the fitness value of each particle is evaluated, and the particles individual local best and global best is updated. The particle position is adjusted as follow; the velocities is computed using Equation \ref{eq:Swarm}. Equation \ref{eq:vmax} is used to scale the velocity to values between 0 and 1 which will serve as a probability that the corresponding bit takes the value of 1. The particles bit vectors are updated by Equation \ref{eq:descrite} according to their velocity which measure the trajectory to the target solution based on local experience ($lbest_{i}$) and global intelligence ($gbest_{i}$). Before the end of the iteration the particle may move to a refined location based on the refine procedure used. 
\begin{algorithm}
\caption{ Discrete Particle Swarm Algorithm }
\label{DPSOalg}
\begin{verbatim}
Initialize 
  1. Generate N particles with M dimensions (P_i...P_N) 
  2. Generate velocities for each particle for M dimension randomly. 
  3. Repeat till Maximum number of iteration OR ErrorThreshold  
         For each particle P_i do the following 
         3.a   Compute fitness  (fitness)
         3.b   Determine Lbest  
               if (lbest_fitness<fitness)
                  3.b.1   lbest=P_i
         3.c      Determine Gbest.
               if (lGest_fitness<fitness)
                  3.c.1   lGest=P_i
         3.d   Compute the Velocity for each dimension using eq.3.2 
         3.e   Bound Velocity using eq.3.4
         3.f   Update particle values using eq. 3.3
         3.g   Refine the location of the particle
         end .
     end 
4. return Gbest
\end{verbatim}
  \end{algorithm}
